---
title: "Homework 6"
author: "yh3429"
date: "2022-12-02"
output: github_document
editor_options: 
  chunk_output_type: console
---
## Problem 1

```{r load_libraries}
library(tidyverse)
library(modelr)
```

To obtain a distribution for $\hat{r}^2$, we'll follow basically the same procedure we used for regression coefficients: draw bootstrap samples; the a model to each; extract the value I'm concerned with; and summarize. Here, we'll use `modelr::bootstrap` to draw the samples and `broom::glance` to produce `r.squared` values. 

```{r weather_df, cache = TRUE}
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2017-01-01",
    date_max = "2017-12-31") %>%
  mutate(
    name = recode(id, USW00094728 = "CentralPark_NY"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  select(name, id, everything())
```


```{r}
weather_df %>% 
  modelr::bootstrap(n = 1000) %>% 
  mutate(
    models = map(strap, ~lm(tmax ~ tmin, data = .x) ),
    results = map(models, broom::glance)) %>% 
  select(-strap, -models) %>% 
  unnest(results) %>% 
  ggplot(aes(x = r.squared)) + geom_density()
```

In this example, the $\hat{r}^2$ value is high, and the upper bound at 1 may be a cause for the generally skewed shape of the distribution. If we wanted to construct a confidence interval for $R^2$, we could take the 2.5% and 97.5% quantiles of the estimates across bootstrap samples. However, because the shape isn't symmetric, using the mean +/- 1.96 times the standard error probably wouldn't work well.

We can produce a distribution for $\log(\beta_0 * \beta1)$ using a similar approach, with a bit more wrangling before we make our plot.

```{r}
weather_df %>% 
  modelr::bootstrap(n = 1000) %>% 
  mutate(
    models = map(strap, ~lm(tmax ~ tmin, data = .x) ),
    results = map(models, broom::tidy)) %>% 
  select(-strap, -models) %>% 
  unnest(results) %>% 
  select(id = `.id`, term, estimate) %>% 
  pivot_wider(
    names_from = term, 
    values_from = estimate) %>% 
  rename(beta0 = `(Intercept)`, beta1 = tmin) %>% 
  mutate(log_b0b1 = log(beta0 * beta1)) %>% 
  ggplot(aes(x = log_b0b1)) + geom_density()
```

As with $r^2$, this distribution is somewhat skewed and has some outliers. 

The point of this is not to say you should always use the bootstrap -- it's possible to establish "large sample" distributions for strange parameters / values / summaries in a lot of cases, and those are great to have. But it is helpful to know that there's a way to do inference even in tough cases. 



## Problem 2

```{r , message = FALSE}
library (tidyverse)
library(ggplot2)
```

##### Read raw data 
```{r}
raw_df = read_csv("./data/homicide-data.csv") 
```
There are 52,179 observations and 12 variables in the raw dataset. And the key variables include `city`, `state`, `dispostion`, and so on. 

##### Data cleaning
```{r}
homicide_df = raw_df %>%
  janitor::clean_names() %>%
  filter (city != "Dallas" & city !="Phoenix"& 
          city != "Kansas City"& city !="Tulsa") %>%  
  filter (victim_race == c("White", "Black")) %>% 
  mutate (city_state = str_c (city, ",", state),
          resolved = as.numeric(disposition == "Closed by arrest"),     
          victim_age = as.numeric(victim_age))


homicide_df
```

##### For the city of Baltimore,MD
```{r}
baltimore_df =
  homicide_df %>% filter (city_state == "Baltimore,MD") %>% 
  select(resolved, victim_age, victim_race, victim_sex)

fit_logi_balt = 
  baltimore_df %>% 
  glm(resolved ~ victim_age + victim_race + victim_sex, data = ., family = binomial()) 

logi_balt_tidy=  
fit_logi_balt %>% 
  broom::tidy() %>% 
  mutate(OR = exp(estimate),
         OR.conf.low = exp(estimate -1.96*std.error),
         OR.conf.high = exp(estimate +1.96*std.error)) %>%
  select(term, log_OR = estimate, OR, OR.conf.low, OR.conf.high ) %>% 
  filter (term == "victim_sexMale")

logi_balt_tidy 
```
So, we can get the adjusted odds ratio comparing male victims to female victims is 0.391 (95% C:0.266, 0.573), keeping all other variables fixed.

##### For each of the cities
```{r}
fit_logi_each =
   homicide_df %>% 
   select(city_state, resolved, victim_age, victim_race, victim_sex) %>% 
   nest (data = -city_state) %>% 
   mutate(models = map(data, ~glm(resolved ~ victim_age + victim_race + victim_sex, 
                                  data = .x, family = binomial())), 
          results = map(models, broom::tidy)) %>% 
  unnest(results) %>% 
   mutate(OR = exp(estimate),
         OR.conf.low = exp(estimate -1.96*std.error),
         OR.conf.high = exp(estimate +1.96*std.error)) %>%
  select(city_state, term, log_OR = estimate, OR, OR.conf.low, OR.conf.high ) %>% 
  filter (term == "victim_sexMale") 


  fit_logi_each 
```

##### Create a plot
```{r}
each_city_pl =
   fit_logi_each %>%  
  mutate(city_state = fct_reorder(city_state, OR)) %>% 
  ggplot (aes(x=city_state, y=OR))+ geom_point()+
  geom_errorbar(aes(ymin=OR.conf.low, ymax=OR.conf.high), width=.2,
                 position=position_dodge(.05)) +
  labs(x = "City, State",
       y = "The estimated ORs",
       title = "The estimated ORs and CIs for each city") +
  theme(axis.text.x = element_text(angle = 65, hjust = 1))
  
each_city_pl
```

Based on the plot, the smallest OR is Baton Rouge, LA and the largest OR is Albuquerque, NM. And there are few cities with the relatively larger confidence intervals, including Long Beach, Fresno, Savannah, Tampa, Richmond, Stockton, and Albuquerque. 
